Analytical reproducibility and data reusability of published meta-analyses on clinical psychological

### 2022-11-17 manuscript.Rmd
Changues for the lastest version

---
title: "Analytical reproducibility of published meta-analyses on clinical psychological
  interventions"
shorttitle: "Meta-analyses reproducibility"
leftheader: "Lopez-Nicolas et al."

author:
 - name: "Rubén López-Nicolás"
   affiliation: "1"
   corresponding: yes
   adress: "Facultad de Psicología, Campus de Espinardo, Universidad de Murcia, edificio n° 31, 30100, Murcia, Spain"
   email: "rlopez@um.es"
 - name: "Daniel Lakens"
   affiliation: "2"
 - name: "Jose A. López-López"
   affiliation: "1"
 - name: "Alejandro Sandoval-Lentisco"
   affiliation: "1"
 - name: "Maria Rubio-Aparicio"
   affiliation: "3"
 - name: "Carmen López-Ibáñez"
   affiliation: "1"
 - name: "Desirée Blázquez-Rincón"
   affiliation: "1"
 - name: "Julio Sánchez-Meca"
   affiliation: "1"

@@

abstract: |
  Nowadays, meta-analysis is one of the most useful and powerful research approaches, however, this relevance relies on its credibility. In recent years different concerns on credibility of psychological research have emerged. Analytical reproducibility of scientific results could be considered as the minimal threshold of it.  In this study, our purpose was to assess the analytical reproducibility of a set of meta-analyses, as well as the reusability of the data as it was available. From a random sample of papers containing at least one meta-analysis on effectiveness of interventions in psychology used in a previous study, 217 meta-analyses were selected. We first tried to retrieve the original data by recovering a data file, recoding the data from document files (pdf, doc) or on request. Second, through a multi-stage workflow, we tried to reproduce the main results of each meta-analysis using these data. The original data were retrieved for 146 meta-analyses from different sources. Of these, in a first stage 52 showed a discrepancy larger than 5% in the main results, in 25 of them this discrepancy was solved with minor adjustments, or correction of coding errors. In the remaining 27, different issues were identified in an in-depth review of the papers, such as: reporting inconsistencies, lack of some data or transcription errors. Current practices of data sharing in meta-analyses hamper the reusability of the meta-analyses. On the other hand, the implementation of new tools would help to avoid certain errors in the meta-analysis reporting process.

@@

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
mask              : no
csl               : "apa.csl"

@@

Nowadays, meta-analysis is widely considered as one of the most useful and powerful research approaches. Given the ongoing growth in the number of scientific publications [@bornmann2021], evidence synthesis approaches -such as meta-analysis- are becoming increasingly relevant. This relevance rests on their credibility, which can be threatened by a lack of rigorous application or poor-quality reporting [@gurevitch2018]. Therefore, given their importance and their role as a useful guide to evidence-based practice, these threats to their credibility need to be closely monitored.
In recent years different concerns on credibility -based on reproducibility and replicability issues- of psychological research -and of other scientific disciplines- have emerged. Several projects have systematically attempted to assess the replicability and reproducibility of different scientific published results (e.g., [@camerer2018; @errington2021a; @klein2014a; @opensciencecollaboration2015]. Those initiatives showed many failures to replicate the published results. In this context, the empirical assessment of scientific published results credibility has become a major task for the scientific community.

There are different approaches to the empirical assessment of scientific credibility or confidence. Reproducibility refers to the attempt to obtain the same results as in the original publication, using the same data and the same analytical procedure. Robustness refers to the assessment of the sensitivity of the originally published results and conclusions to variations in the original analytical strategy using the same data. Replicability is a core principle of the scientific method and refers to the fact that the same scientific evidence should be observed when independent researchers try to answer the same research question from the same approach at different moments using different data. In other words, obtaining the same results, using different data and answering the same question [@nationalacademiesofsciencesengineeringandmedicine2019; @nosek2022]. In this project we focus on the reproducibility of meta-analyses.

The reproducibility of all published scientific results could be considered as the minimal threshold of scientific credibility [@hardwicke2021]. Different approaches can be adopted for the empirical assessment of reproducibility, for instance @nosek2022 make the distinction between process reproducibility and outcome reproducibility. Following this framework, a process reproducibility assessment could be carried out reviewing the availability of the materials, data, and precise details of the analytical strategy in the report or in an analysis script file required to proceed with the reproduction attempt. On the other hand, an outcome reproducibility assessment would be carried out when the required elements are retrievable, and the reproduction attempt proceeds. It is worth noting that, depending on how the analytical details are available, the challenges, implications and workload of these outcome reproducibility checks are different. The availability of the original analysis script code (i.e., the original computational instructions in a programming language) facilitates reproducibility analysis by simply re-running it, although this is seldom available [@hardwicke2020; @hardwicke2022; @lopez-nicolas2021]. When only a summary is available in the research reports (which is the most common scenario in practice), a task of reconstruction of the original analysis scheme is required. The challenges and implications of failed reproductions in both cases may be of a different nature.

In the meta-analytic arena, some reproducibility attempts have been carried out in recent years. For instance, some process reproducibility assessments have shown an important lack of data availability in machine-readable formats, and an almost complete absence of analysis script code availability [@lopez-nicolas2021; @polanin2020]. Furthermore, some outcome reproducibility assessments have shown a considerable number of failures when trying to reproduce the primary effect sizes of some published meta-analyses by recollecting primary data from primary studies [@gotzsche2007; @maassen2020; @tendal2009] possibly due to lack of details on how primary effect sizes were selected and computed. In these outcome reproducibility studies, the main task entails reconstructing the original data by retrieving them from the source, namely the included primary studies. Thus, their assessment focus is on this stage of the analysis pipeline of a meta-analysis, which usually involves decisions on how to deal with the multiplicity of effects in the primary studies and the computation process of standardized effect sizes.

Usually, reproducibility studies use the original data available from the original authors (e.g., [@artner2020; @hardwicke2021; @hardwicke2018]. This puts the focus of the assessment at a different stage of the research pipeline: reusability of the available data, challenges for the reconstruction of the original analysis scheme, reporting errors, etc. Therefore, in order to carry out a reproducibility analysis in this way, the original data must be available. Although data availability seems to have improved in the last years [@hardwicke2018; @tedersoo2021; @wallach2018], systematic reviews and meta-analyses appear to be a special case. Typically, the data collected for a meta-analysis is study-level summary data extracted from published primary studies and is commonly reported in the paper itself through tables or forest plots. This may lead to the idea that common data sharing practices do not apply to meta-analysis. For instance, @page2022 analysed the content of data availability statements from a set of meta-analyses published in 2020. Only 31% included a data availability statement and only 13% of these included a link to access the data openly, with 23% stating that all relevant data are available in the paper itself, 10% stating that data sharing is no applicable as no datasets were generated, 8% stating that data sharing is no applicable as the data is drawn from already published literature, and 42% stating that data were available upon request. It is surprising that, even just considering meta-analyses that included a data availability statement, some of them assume that such practices do not apply to meta-analyses or that the data in the article itself is sufficient.

## Purpose 
Previous research has revealed that there is room for improvement at different stages of the meta-analytic process pipeline. In this study our purpose is twofold. First, we broadened previous process reproducibility assessments by considering the possible availability of the data upon request to the original authors and by assessing the reusability of the meta-analytic data in the different formats in which they are usually available. Second, we verified the outcome reproducibility of the meta-analyses that were process-reproducible using the available data. We attempted to explore meta-analysis outcome reproducibility at a different stage or level than previous work that is more focused on primary effect sizes reproducibility, using the primary effects sizes already coded by the original authors.

@@

# Method

The pre-data analysis protocol (https://osf.io/42r3p/) was pre-registered on 19 October 2021. Any deviation from this protocol is explicitly acknowledged.

## Identification and selection of articles and meta-analyses 
In previous research we identified a pool of published meta-analytic reports on clinical psychological interventions through a systematic electronic search [@lopez-nicolas2021]. Of this pool, 100 were randomly selected using a random number generator between 1 and the total number of meta-analyses identified. The full search strategies and a summary of the screening process are available at: https://osf.io/z5vrn/, and the workflow of the randomly selection process is available at: https://osf.io/cp293/.
From these 100 articles, each independent reported meta-analysis with at least 10 primary studies was selected. In case no meta-analysis reported in a paper had at least 10 studies, the meta-analysis with the highest number of primary studies was selected, even if this meta-analysis integrated less than 10 studies. `r Words(n_mas_less_10)` of the articles included in this report were in this situation. Therefore, our unit of analysis was each independent meta-analysis selected under these criteria. A total of `r n_mas_total` independent meta-analyses were selected.

## Retrieval of primary data
The availability of necessary primary data was checked. First, we looked for machine-readable data files through links leading to third-party repositories or in supplementary material hosted by the journal. Secondly, we looked for available data through tables or forest plots in document format in the meta-analytic report itself or supplementary material. In these cases, the primary data had to be manually re-coded to reuse it. On the other hand, if the primary data of a meta-analysis were not directly available, neither in a data file nor in a document file, we attempted to obtain the data through request to the corresponding author identified in the associated paper. We sent an initial request in June 2021 and a subsequent reminder in October 2021 if no reply was received. This reminder was sent to a more recent alternative email address if we were able to find one. If we were unable to obtain the data through the email request, the associated meta-analysis was labelled as not process reproducible. 
In order to be able to reproduce meta-analyses, mainly primary effects and their associated standard errors are required. These are generally computed from primary statistics retrieved from the primary studies such as means, standard deviations or sample sizes. In this sense, we tried to retrieve the least processed data possible. First, we sought for the primary statistics, recovered in `r sprintf("%0.0f%%", df_type_of_data$perc[3] * 100)` of the cases; second, we sought for the primary effects and their standard errors (or, alternatively, the sampling variances), recovered in `r sprintf("%0.0f%%", df_type_of_data$perc[2] * 100)` of the cases; finally, we sought for the primary effects and their confidential limits, recovered in `r sprintf("%0.0f%%", df_type_of_data$perc[1] * 100)` of the cases, from which the standard errors were approximated as follows:

@@

with $se_i$ being the standard error of the ith effect size, $UB_i$ and $LB_i$ the upper and lower confidence limits of confidence interval for the ith effect size, and $z_{\alpha/2}$ the $1 - z_{\alpha/2}$ quantile of the standard normal distribution (usually, $z_{\alpha/2} = 1.96$ assuming a 95% confidence interval).

## Reconstructing the original analytical scheme
To proceed with reproducibility attempts of the meta-analyses that were labelled as process reproducible, we first looked for the availability of the original analysis script. When it was available, analytical reproducibility was checked by rerunning the original script on the associated primary data. In most cases (`r sprintf("%0.0f%%", 100-((n_mas_w_script/df_process_rep$n[2]) * 100))`), the analysis script code was not available. Thus, in these cases we tried to reconstruct the original analytical scheme using the technical details reported in the paper. Specifically, we collected information on: (a) meta-analytic model originally assumed; (b) weighting scheme; (c) between-studies variance estimator; (d) confidence interval method; and (e) software used.  If any of these details about the analytical methods were not reported, but the software used was mentioned, we inferred the first four pieces of information from the default settings of the software used. If the software used was not reported, we inferred this information from the default settings of the most used software in the sample, which was *Comprehensive Meta-Analysis*. Additional information about the meta-analysis was collected that is not reported in this manuscript. The full list of variables collected is available in the Protocol (https://osf.io/tq4uf/) and a Codebook describing these variables is available at: https://osf.io/ym78s/.

## Data collection procedure 
Primary-level data and aggregate-level data described above, were coded by five members of the group. At a first pilot stage, a random sample of five articles of the total pool was independently coded by the five members and, subsequently, in a series of meetings, disagreements between the coders were resolved by consensus. Next, the initial pool of 100 included articles was split among four of them, 25 each. A random sample of 25 articles of the total pool was assigned to the fifth member to carry out independent double-coding of these cases, with the goal to track the reliability of the data collection process. Disagreements were resolved by consensus and checking the original materials.

## Reproducibility outcomes
Each meta-analysis was labelled using the following reproducibility success scheme: (a) reproducible; (b) not process-reproducible; (c) numerical error (d) decision error. Not process-reproducible refers to situations when we were unable to access the primary data neither through direct extraction nor upon request. Similar to previous studies (Artner et al., 2020; Hardwicke et al., 2018, 2021) an index of numerical error was computed (see Protocol https://osf.io/tq4uf/). This index expressed the differences between reproduced and original values as percentages. To avoid labelling minor numerical discrepancies related to numerical rounding as reproducibility problems, a 5% discrepancy threshold was set. Thus, a meta-analysis was labelled as numerical error if showed a discrepancy larger than 5%. 
Finally, decision error refers to situations where the $p_{reported}$ falls on the opposite side of the .05 boundary in relation to the $p_{reproduced}$. 
We mainly focused on analytical reproducibility of summary effects, their confidence bounds and the result of the null hypothesis significance test. Secondarily, we also assessed analytical reproducibility of other synthesis methods such as heterogeneity statistics.

## Reproducibility checks workflow 
Analytical reproducibility checks were carried out at different stages. Firstly, through reported analytic details or script code. When the analysis script code was available, computational reproducibility was checked by rerunning the script with the available primary data. In most cases, the analysis script code was not available. Thus, in these cases we coded the analytic details as explained above to fit equivalent meta-analytic models as a function of these details using the available primary data. This analysis scheme was programmed in the R environment [@r2022] using the *metafor* package [@viechtbauer2010]. The scripts are available at: …. 
Second, given that the manual recoding process is an error-prone task, some mistakes can appear. Thus, those meta-analyses labelled as numerical error and/or decision error in the previous stage were re-assessed by a different member of the team. In cases where an error was found in the originally coded results, analytic methods and/or primary data, the meta-analyses were reproduced again and re-labelled according to the updated results. 
Third, a qualitative assessment of the meta-analyses still labelled as numerical error and/or decision error was carried out. The same reviewers who checked for errors produced individual reports on the possible source of the discrepancy and its reproducibility was judged qualitatively by four of the other authors. This stage was a deviation from the pre-registered protocol, and made it possible to identify situations with obvious explanations, such as rounding, inverted signs, etc.
Finally, for meta-analyses that remained labelled as non-reproducible, an email was sent to the corresponding author of the associated paper explaining our aims, our approach, and our results regarding his/her meta-analysis and requesting additional information that could explain the mismatch between the original reported results and the reproduced results. We tried to solve the reproducibility issues within a month after the request and we updated the label accordingly.

@@

From the 100 included papers, `r n_mas_total` independent meta-analyses were selected following the criteria explained above. These meta-analyses included `r round(k_mean, 2)` primary studies on average (`r sprintf("sd = %0.2f; median = %0.0f; interquartile range = %0.0f-%0.0f; range = %0.0f-%0.0f)", k_sd, k_median, k_q1, k_q3, range[1], range[2])`). Figure 1 displays the distribution of number of primary studies among the meta-analyses included in our sample. Original results and characteristics of these meta-analyses are available at: …

@@

## Process reproducibility 
Figure 2 summarizes the primary data retrieval results. Based on the availability of primary data, either retrieved directly from the paper or upon request, `r df_process_rep$n[2]` meta-analyses (`r sprintf("%0.0f%%", df_process_rep$perc[2]*100)`, see Fig. 2a) were labelled as process reproducible. Of these `r df_process_rep$n[2]` meta-analyses, in about half of the cases the primary data was retrieved from a forest plot in the paper itself and in about a third of the cases the primary data was retrieved from supplementary files. Only in `r sprintf("%0.0f%%", df_source_primary_data$perc[1]*100)` of the cases the primary data was retrieved upon request (see Fig. 2b for further details). Although attempts were made to retrieve data for `r df_process_rep$n[1]+df_source_primary_data$n[1]` meta-analyses from `r sum(df_request$n)` different papers, data was only retrieved upon request for `r df_source_primary_data$n[1]` of them, from `r df_request$n[2]` different papers (`r sprintf("%0.0f%%", df_request$perc[2]*100)`, see Fig. 2c). In the remaining cases, a reply providing some reasons not to share was received in about a third of the cases (`r sprintf("%0.0f%%", df_request$perc[2]*100)`, see Fig 2c), whereas no reply was received in the rest. Table 1 summarises the different reasons given in cases where data was not provided upon request.

@@

## Challenges faced retrieving primary data
In most cases, when the necessary data was available, such data was in document formats, as previously reported. Data available in tables or forest plots shared in *pdf* or *docx* format –either in the document itself or in the supplementary materials– was found to be highly prevalent. This led to a manual recoding of the primary data to be able to reuse them. Furthermore, when data was reported through general tables (i.e. tables listing all the primary studies included with their characteristics), it was not always obvious in which meta-analysis each data entry was included, leading to the time-consuming task of matching each data entry with each independent meta-analytic result reported in the paper. There were only `r df_source_primary_data$n[2]` meta-analyses (from`r sum(df_data_downloaded$Item)` different papers) of the `r df_process_rep$n[2]` labelled as process reproducible (`r sprintf("%0.0f%%", df_source_primary_data$perc[2]*100)`), where the task of retrieving the data required simply downloading the data in an machine-readable data file format.
On the other hand, as shown in Figure 2c, when the necessary data was not available, retrieving it upon request to the original authors led to a remarkably low success rate.

@@

 figure2

@@

## Outcome reproducibility 
The outcome reproducibility was checked in `r df_process_rep$n[2]` meta-analyses from `r nrow(df_nmas_wdata)` different papers. In `r filter(df_script, script == 1)$n` of these meta-analyses (`r sprintf("%0.0f%%", filter(df_script, script == 1)$n/sum(df_script$n)*100)`), all from the same paper, the original script code was available. Therefore, in these five cases, analytical reproducibility was checked running the original script analysis on the original primary data. In the remaining cases, the original analytical framework was reconstructed as explained above. 
```{r first_stage, include=FALSE}

>>>>

---
title: "Analytical reproducibility and data reusability of published meta-analyses on clinical psychological
  interventions"
shorttitle: "Meta-analyses reproducibility"
leftheader: "Lopez-Nicolas et al."

author:
 - name: "Rubén López-Nicolás"
   affiliation: "1"
   corresponding: yes
   adress: "Facultad de Psicología, Campus de Espinardo, Universidad de Murcia, edificio n° 31, 30100, Murcia, Spain"
   email: "rlopez@um.es"
 - name: "Daniel Lakens"
   affiliation: "2"
 - name: "Jose A. López-López"
   affiliation: "1"
 - name: "Maria Rubio-Aparicio"
   affiliation: "3"
 - name: "Alejandro Sandoval-Lentisco"
   affiliation: "1"
 - name: "Carmen López-Ibáñez"
   affiliation: "1"
 - name: "Desirée Blázquez-Rincón"
   affiliation: "1"
 - name: "Julio Sánchez-Meca"
   affiliation: "1"

@@

abstract: |
  Meta-analysis is one of the most useful and powerful research approaches, however, this relevance relies on its credibility. In recent years different concerns on credibility of psychological research have emerged. Analytical reproducibility of scientific results could be considered as the minimal threshold of it.  In this study, our purpose was to assess the analytical reproducibility and data reusability of a set of published meta-analyses. From a random sample of 100 papers containing at least one meta-analysis on effectiveness of interventions in psychology used in a previous study, 217 meta-analyses were selected. We first tried to retrieve the original data by recovering a data file, recoding the data from document files (pdf, doc) or on request. Second, through a multi-stage workflow, we tried to reproduce the main results of each meta-analysis using these data. The original data were retrieved for 146 meta-analyses from different sources. Of these, in a first stage 52 showed a discrepancy larger than 5% in the main results, in 25 of them this discrepancy was solved with minor adjustments, or correction of coding errors. In the remaining 27, different issues were identified in an in-depth review of the papers, such as: reporting inconsistencies, lack of some data or transcription errors. Current practices of data sharing in meta-analyses hamper the reusability of meta-analytic data. On the other hand, the implementation of new tools would help to avoid certain errors in the meta-analysis reporting process.

@@

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
mask              : no
csl               : "apa.csl"
nocite            : |
                    @koffel016, @maggio2011, @nguyen2022, @page2018, @page2016, @tendal2011, @wayant2019

@@

Meta-analysis is widely considered as an important approach to evaluate a body of work. Given the ongoing growth in the number of scientific publications [@bornmann2021], evidence synthesis approaches -such as meta-analysis- are becoming increasingly relevant for a cumulative science. This relevance rests on the credibility of meta-analytic results, which can be threatened by a lack of rigorous application or poor-quality reporting [@gurevitch2018]. Given the importance of meta-analyses for evidence-based practice, these threats to their credibility need to be closely monitored.
In recent years different concerns on credibility of  empirical claims have emerged. Several projects have systematically attempted to assess the replicability and reproducibility of published scientific results (e.g., @artner2020; @errington2021a; @opensciencecollaboration2015). Those initiatives showed many failures to replicate or reproduce the published results. In this context, the empirical assessment of scientific published results credibility has become a major task for the scientific community.

There are different approaches to the empirical assessment of scientific credibility. Reproducibility refers to the attempt to obtain the same results as in the original publication, using the same data and the same analytical procedure. Robustness refers to the assessment of the sensitivity of the originally published results and conclusions to variations in the original analytical strategy using the same data. Replicability is a core principle of the scientific method and refers to the fact that the same scientific evidence should be observed when independent researchers try to answer the same research question from the same approach at different moments using different data. In other words, obtaining the same results, using different data and answering the same question [@nationalacademiesofsciencesengineeringandmedicine2019; @nosek2022]. In this project, we focus on the reproducibility of meta-analyses.

The reproducibility of all published scientific results could be considered as the minimal threshold of scientific credibility [@hardwicke2021]. Different approaches can be adopted for the empirical assessment of reproducibility. For example @nosek2022 make the distinction between process reproducibility and outcome reproducibility. Following this framework, a process reproducibility assessment could be carried out by reviewing the availability of the materials, data, and precise details of the analytical strategy in the report that are required to proceed with the reproduction attempt. An outcome reproducibility assessment can be carried out when the required elements are retrievable by actually reproducing the analyses. It is worth noting that the difficulty of performing an outcome reproducibility assessment depends on which analytical information is available. The availability of the original analysis code (i.e., the original computational instructions in a programming language) facilitates reproducibility analysis by enabling simply re-running the code on the data. Regrettably, the analysis code is currently seldom available [@hardwicke2020; @hardwicke2022; @lopez-nicolas2021]. When only a verbal summary of the performed analyses is available in the research report (which is the most common scenario in practice), the original analysis needs to be reconstructed. The challenges and implications of failed reproductions in both cases may be of a different nature.

Several reproducibility analyses of meta-analyses have been performed in recent years. For example, some process reproducibility assessments have shown an important lack of data availability in machine-readable formats, and an almost complete absence of analysis script code availability [@lopez-nicolas2021; @polanin2020]. Furthermore, some outcome reproducibility assessments have shown a considerable number of failures when trying to reproduce the primary effect sizes of some published meta-analyses by recollecting primary data from primary studies [@gotzsche2007; @maassen2020; @tendal2009] possibly due to lack of details on how primary effect sizes were selected and computed. In these outcome reproducibility studies, the main task entails reconstructing the original data by retrieving them from the source, namely the included primary studies. Thus, their assessment focus is on this stage of the analysis pipeline of a meta-analysis, which usually involves decisions on how to select the primary outcomes and how to deal with possible dependency, and the computation of (standardized) effect sizes. Figure 1 displays a summary of the basic meta-analysis pipeline through a flowchart, outlining the different stages and listing previous work that has explored different facets of reproducibility of these as well as the required elements to be able to reproduce each stage.

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth, height=\textheight]{results/Figure 1.png}

\caption{Flowchart displaying the basic pipeline of a meta-analysis. Each of the stages may be subject to reproducibility evaluation. On the left, known studies that have evaluated some facet of the reproducibility of each stage are listed. On the right, the various elements that must be available to reproduce each stage are enumerated.
}

\label{fig:figs1}
\end{center}
\end{figure*}

Reproducibility analysis typically uses the original data available from the original authors (e.g., [@artner2020; @hardwicke2021; @hardwicke2018]. This puts the focus of the assessment at factors such as the reusability of the available data, challenges for the reconstruction of the original analysis scheme, reporting errors, etc.   Although data availability seems to have improved in the last years [@hardwicke2018; @tedersoo2021; @wallach2018], systematic reviews and meta-analyses appear to be a special case. Typically, the data collected for a meta-analysis is study-level summary data extracted from published primary studies which is commonly reported in the paper through tables or forest plots. This may lead to the idea that common data sharing practices do not apply to meta-analysis. For example, @page2022 analysed the content of data availability statements from a set of meta-analyses published in 2020. Only 31% included a data availability statement and only 13% of these included a link to access the data openly, with 23% stating that all relevant data are available in the paper itself, 10% stating that data sharing is not applicable as no datasets were generated, 8% stating that data sharing is not applicable as the data is drawn from already published literature, and 42% stating that data were available upon request. It is surprising that, even just considering meta-analyses that included a data availability statement, the authors of these meta-analysis  assume that such practices do not apply to meta-analyses or that the data in the article itself is sufficient.

## Purpose 
Previous research has revealed that there is room for improvement at different stages of the meta-analytic process pipeline. In this study our purpose is twofold. First, we broadened previous process reproducibility assessments by considering data availability on request and by contacting original authors to request required information to reproduce the meta-analysis. Second, we verified the outcome reproducibility of the meta-analyses that were process-reproducible using the available data. Where previous work focussed on the reproducibility of primary effect sizes, we explored meta-analysis outcome reproducibility using the primary effects sizes already coded by the original authors.

@@

# Method
## Preregistration
The pre-data analysis protocol (https://osf.io/42r3p/) was pre-registered on 19 October 2021. Any deviation from this protocol is explicitly acknowledged.

## Data, materials, and online resources

## Identification and selection of articles and meta-analyses 
In previous research we identified a pool of 664 meta-analytic reports on clinical psychological interventions published between 2000 and 2020 through a systematic electronic search [@lopez-nicolas2021]. Of this pool, 100 were randomly selected using a random number generator between 1 and the total number of meta-analyses identified. The full search strategies and a summary of the screening process are available at: https://osf.io/z5vrn/, and the workflow of the random selection process is available at: https://osf.io/cp293/.
From these 100 articles, each independent reported meta-analysis with at least 10 primary studies was selected. In case no meta-analysis reported in a paper had at least 10 studies, the meta-analysis with the highest number of primary studies was selected, which was the case for `r n_mas_less_10` of the articles included in this report. Our unit of analysis was each independent meta-analysis selected under these criteria. A total of `r n_mas_total` independent meta-analyses were selected.

## Retrieval of primary data
The availability of necessary primary data was checked. First, we searched for machine-readable data files through links leading to third-party repositories or in supplementary material hosted by the journal. Second, we looked for available data through tables or forest plots in the meta-analytic report itself, or in supplementary material. In these cases, the primary data had to be manually re-coded to reuse it. Finally, if the primary data of a meta-analysis were not directly available after the previous steps, we attempted to obtain the data through a request to the corresponding author identified in the associated paper. We sent an initial request in June 2021 and, if there was no reply, a subsequent reminder in October 2021. This reminder was sent to a more recent alternative email address if we were able to find one. If we were unable to obtain the data through the email request, the associated meta-analysis was labelled as not process reproducible.  
In order to be able to reproduce meta-analyses, primary effects and their associated standard errors are required. These are generally computed from primary statistics retrieved from the primary studies such as means, standard deviations or sample sizes. We attempted to retrieve the least processed data possible. First, we sought for the primary statistics, recovered in `r sprintf("%0.0f%%", df_type_of_data$perc[3] * 100)` of the cases. Second, we sought for the primary effects and their standard errors (or, alternatively, the sampling variances), recovered in `r sprintf("%0.0f%%", df_type_of_data$perc[2] * 100)` of the cases. Finally, we sought for the primary effects and their confidential limits, recovered in `r sprintf("%0.0f%%", df_type_of_data$perc[1] * 100)` of the cases, from which the standard errors were approximated as follows:

@@

with $se_i$ being the standard error of the ith effect size, $UB_i$ and $LB_i$ the upper and lower confidence limits of confidence interval for the ith effect size, and $z_{\alpha/2}$ the $1 - z_{\alpha/2}$ quantile of the standard normal distribution (usually, $z_{\alpha/2} = 1.96$ assuming a two-sided 95% confidence interval).

## Reconstructing the original analytical scheme
To proceed with reproducibility attempts of the meta-analyses that were labelled as process reproducible, we first looked for the availability of the original analysis script. When it was available, analytical reproducibility was checked by rerunning the original script on the associated primary data. In `r df_process_rep$n[2] -  n_mas_w_script` cases (`r sprintf("%0.0f%%", 100-((n_mas_w_script/df_process_rep$n[2]) * 100))`), the analysis script code was not available. In these cases we tried to reconstruct the original analytical scheme using the technical details reported in the paper. Specifically, we collected information on: (a) the meta-analytic model originally assumed; (b) the weighting scheme; (c) the between-studies variance estimator; (d) the method used to compute the confidence interval; and (e) the software used to perform the meta-analysis. If any of these details about the analytical methods were not reported, but the software used was mentioned, we inferred the first four pieces of information from the default settings of the software used. If the software used was not reported, we inferred this information from the default settings of the most used software in the sample, which was *Comprehensive Meta-Analysis*. Additional information about the meta-analysis was collected that is not reported in this manuscript. The full list of variables collected is available in the Protocol (https://osf.io/tq4uf/) and a Codebook describing these variables is available at: https://osf.io/ym78s/.

## Data collection procedure 
Primary-level data and aggregate-level data described above were coded by five members of the group. At a first pilot stage, a random sample of five articles of the total pool was independently coded by the five members and, subsequently, in a series of meetings, disagreements between the coders were resolved by consensus. Next, the initial pool of 100 included articles was split among four coders, 25 articles each. A random sample of 25 articles of the total pool was assigned to the fifth member to carry out independent double-coding, with the goal to examine the reliability of the data collection process. Disagreements were resolved by consensus and by double-checking the original materials.

## Reproducibility outcomes
Each meta-analysis was labelled using the following reproducibility success scheme: (a) reproducible; (b) not process-reproducible; (c) numerical error, and (d) decision error. Not process-reproducible refers to situations where we were unable to access the primary data neither through direct extraction nor upon request. Similar to previous studies (Artner et al., 2020; Hardwicke et al., 2018, 2021) an index of numerical error was computed (see Protocol https://osf.io/tq4uf/). This index expressed the difference between reproduced and original values as a percentage. To avoid labelling minor numerical discrepancies related to numerical rounding as reproducibility problems, a 5% discrepancy threshold was set. Thus, a meta-analysis was labelled as 'numerical error' if it showed a discrepancy larger than 5%.^[A sensitivity analysis using other possible criteria is reported in the supplementary file.] 
Finally, the label 'decision error' refers to situations where the $p_{reported}$ fell on the opposite side of the .05 boundary in relation to the $p_{reproduced}$. 
We focus on analytical reproducibility of summary effects, their confidence bounds and the result of the null hypothesis significance test. Secondarily, we also assessed analytical reproducibility of other synthesis methods such as heterogeneity statistics.

## Reproducibility checks workflow 
Analytical reproducibility checks were carried out at different stages. First, through reported analytic details or script code. When the analysis script code was available, computational reproducibility was checked by rerunning the script with the available primary data. In most cases, the analysis script code was not available. Thus, in these cases we coded the analytic details as explained above to fit equivalent meta-analytic models as a function of these details using the available primary data. This analysis scheme was programmed in the R environment [@r2022] using the *metafor* package [@viechtbauer2010]. The scripts are available at: ….

Second, given that the manual recoding process is an error-prone task, some mistakes can appear. Thus, those meta-analyses labelled as numerical error and/or decision error in the previous stage were re-assessed by a different member of the team. In cases where an error was found in the originally coded results, analytic methods and/or primary data, the meta-analyses were once reproduced again and re-labelled according to the updated results. Additionally, a qualitative assessment of the meta-analyses still labelled as numerical error and/or decision error was also carried out. The same reviewers who checked for errors produced individual reports on the possible source of the discrepancy and its reproducibility was judged qualitatively by four of the other authors. This stage was a deviation from the pre-registered protocol, and made it possible to identify situations with obvious explanations, such as rounding issues, inverted signs, etc.

Finally, for meta-analyses that remained labelled as non-reproducible, an email was sent to the corresponding author of the associated paper explaining our aims, our approach, and our results regarding his/her meta-analysis and requesting additional information that could explain the mismatch between the original reported results and the reproduced results. We tried to solve the reproducibility issues within a month after the request and we updated the label accordingly.

@@

From the 100 included papers, `r n_mas_total` independent meta-analyses were selected following the criteria explained above. These meta-analyses included `r round(k_mean, 2)` primary studies on average (`r sprintf("sd = %0.2f; median = %0.0f; interquartile range = %0.0f-%0.0f; range = %0.0f-%0.0f)", k_sd, k_median, k_q1, k_q3, range[1], range[2])`). Figure 2 displays the distribution of number of primary studies among the meta-analyses included in our sample. Original results and characteristics of these meta-analyses are available at: …

@@

## Process reproducibility 
Figure 3 summarizes the primary data retrieval results. Based on the availability of primary data, either retrieved directly from the paper or upon request, `r df_process_rep$n[2]` meta-analyses (`r sprintf("%0.0f%%", df_process_rep$perc[2]*100)`, see Fig. 2a) were labelled as process reproducible. Of these `r df_process_rep$n[2]` meta-analyses, in about half of the cases the primary data was retrieved from a forest plot in the paper itself and in about a third of the cases the primary data was retrieved from supplementary files. Only in `r sprintf("%0.0f%%", df_source_primary_data$perc[1]*100)` of the cases the primary data was retrieved upon request (see Fig. 2b for further details). Although attempts were made to retrieve data for `r df_process_rep$n[1]+df_source_primary_data$n[1]` meta-analyses from `r sum(df_request$n)` different papers by emailing the corresponding authors, data was only retrieved for `r df_source_primary_data$n[1]` meta-analyses, from `r df_request$n[2]` different papers (`r sprintf("%0.0f%%", df_request$perc[2]*100)`, see Fig. 2c). For the remaining `r df_process_rep$n[1]` from `r df_request$n[1] + df_request$n[3]` different papers, a reply providing some reasons not to share was received in `r sprintf("%0.0f%%", df_request$perc[2]*100)` (see Fig 2c), whereas no reply was received for the remainder of the meta-analyses. Table 1 summarises the different reasons corresponding authors given when data was not provided upon request.

@@

## Challenges faced retrieving primary data
In most cases, when the meta-analytic data was available, it was shared in document formats, as previously reported. Data available in tables or forest plots shared in *pdf* or *docx* format –either in the document itself or in the supplementary materials– was found to be highly prevalent. This required a manual recoding of the primary data to be able to reuse them. Furthermore, when data was reported through general tables (i.e. tables listing all the primary studies included with their characteristics), the meta-analysis associated with each data entry was not always obvious, leading to the time-consuming task of matching each data entry with each independent meta-analytic result reported in the paper. There were only `r df_source_primary_data$n[2]` meta-analyses (from `r words(sum(df_data_downloaded$Item))` different papers) of the `r df_process_rep$n[2]` meta-analyses labelled as process reproducible (`r sprintf("%0.0f%%", df_source_primary_data$perc[2]*100)`), where the task of retrieving the data required simply downloading the data in an machine-readable data file format.
On the other hand, as shown in Figure 3c, when the necessary data was not available, retrieving it upon request to the original authors led to a remarkably low reponse rate.

@@

 figure3

@@

## Outcome reproducibility 
The outcome reproducibility was checked in `r df_process_rep$n[2]` meta-analyses from `r nrow(df_nmas_wdata)` different papers. As mentioned above, in `r filter(df_script, script == 1)$n` of these meta-analyses (`r sprintf("%0.0f%%", filter(df_script, script == 1)$n/sum(df_script$n)*100)`), all from the same published article, the original script code was available. Therefore, in these five cases, analytical reproducibility was checked running the original analysis script on the original primary data. In the remaining cases, the original analytical framework was reconstructed as explained in the method section. 
```{r first_stage, include=FALSE}
